---
title: "Notes for Atika"
author: "Jonathan A. Pedroza"
date: "4/17/2020"
output:
  word_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Manipulation & Proposed Models
```{r package and other specs, include = FALSE}

library(tidyverse)
library(inspectdf)
library(psych)
library(lme4)
library(lmerTest)
library(optimx)

options(max.print = 99999)
options(scipen = 999)
theme_set(theme_minimal())


getwd()

set.seed(04092020)
```

```{r data upload, echo = FALSE, eval = TRUE}

county16 <- read_csv("C:/Users/cpppe/OneDrive/Desktop/github shared projects/dissertation/final_data/county16_sub.csv")
county17 <- read_csv("C:/Users/cpppe/OneDrive/Desktop/github shared projects/dissertation/final_data/county17_sub.csv")
county18 <- read_csv("C:/Users/cpppe/OneDrive/Desktop/github shared projects/dissertation/final_data/county18_sub.csv")
county19 <- read_csv("C:/Users/cpppe/OneDrive/Desktop/github shared projects/dissertation/final_data/county19_sub.csv")
county20 <- read_csv('C:/Users/cpppe/OneDrive/Desktop/github shared projects/dissertation/final_data/county20_sub.csv')
```

```{r data reduction, echo = FALSE, eval = TRUE}

county16_sub <- county16[, -which(colMeans(is.na(county16)) >= 0.40)]
county17_sub <- county17[, -which(colMeans(is.na(county17)) >= 0.40)]
county18_sub <- county18[, -which(colMeans(is.na(county18)) >= 0.40)]
county19_sub <- county19[, -which(colMeans(is.na(county19)) >= 0.40)]
county20_sub <- county20[, -which(colMeans(is.na(county20)) >= 0.40)]

county <- full_join(county16_sub, county17_sub)
county <- full_join(county, county18_sub)
county <- full_join(county, county19_sub)
county <- full_join(county, county20_sub)

county %>% 
  inspect_na() %>% 
  show_plot()

county <- county[, -which(colMeans(is.na(county)) >= .25)]

county %>% 
  names()

county <- county %>% 
  dplyr::select(rowid,
                state_fips_code:release_year,
                poor_or_fair_health:access_to_exercise_opportunities,
                preventable_hospital_stays,
                some_college:driving_alone_to_work,
                food_insecurity:uninsured_children,
                median_household_income:percent_rural) %>% 
  rename(state = state_abbreviation,
         year = release_year)

county %>% 
  inspect_na() %>% 
  show_plot()

county <- county %>% 
  dplyr::select(-percent_non_hispanic_african_american,
                -percent_american_indian_and_alaskan_native,
                -motor_vehicle_crash_deaths,
                -residential_segregation_non_white_white)

county <- county %>% 
  mutate(phyact_percent = (physical_inactivity*100),
         ltpa_percent = (100 - phyact_percent)) %>% 
  rename(access_pa = access_to_exercise_opportunities)
```

# Data Descriptives 

Notes: 
[rpsychologist multi-level modeling, including growth models](https://rpsychologist.com/r-guide-longitudinal-lme-lmer)
[penn state's growth models basics](https://rpsychologist.com/r-guide-longitudinal-lme-lmer)

1. Look into the change of access to physical activity opportunities over time.
```{r, echo = FALSE, eval = TRUE}
county %>% 
  drop_na() %>% 
  ggplot(aes(access_pa*100)) +
  geom_histogram(color = 'white', fill = 'dodgerblue', bins = 20) +
  facet_wrap(~year) +
  labs(x = 'Access to Physical Activity Opportunities Percentage',
       y = 'Count',
       title = 'Count of Access to Physical Activity Opportunities')

county %>% 
  drop_na() %>% 
  group_by(year) %>% 
  mutate(access_percent = access_pa*100) %>% 
  summarize(mean_percent = mean(access_percent)) %>% 
  ggplot(aes(year, mean_percent)) +
  geom_line(color = 'dodgerblue', size = 1) +
  geom_point() + 
  scale_y_continuous(name = 'Access (%)',
                     limits = c(60, 70))

```

2. Look into the chnage of leisure-time physical activity engagement over time.
```{r, echo = FALSE, eval = TRUE}
# View(county)

county %>% 
  drop_na() %>% 
  ggplot(aes(ltpa_percent)) +
  geom_histogram(color = 'white', fill = 'dodgerblue', bins = 20) +
  facet_wrap(~year) +
  labs(x = 'Leisure Time Physical Activity Engagement',
       y = 'Count',
       title = 'Count of Leisure Time Physical Activity Engagement')

county %>% 
  drop_na() %>% 
  group_by(year) %>% 
  summarize(mean_percent = mean(ltpa_percent)) %>% 
  ggplot(aes(year, mean_percent)) +
  geom_line(color = 'dodgerblue', size = 1) +
  geom_point() +
  scale_y_continuous(name = 'Leisure-Time Physical Activity (%)',
                     limits = c(70, 80))
```

3. Look into the role of percent latino
```{r, echo = FALSE, eval = TRUE}
# names(county)

# describeBy(county$percent_hispanic, group = county$year)

county$latino_group <- cut(county$percent_hispanic, breaks = 3)

county %>% 
  group_by(year) %>% 
  count(latino_group)

county %>% 
  dplyr::select(year, percent_hispanic, access_pa, ltpa_percent, latino_group) %>% 
  drop_na() %>% 
  group_by(year) %>% 
  mutate(access_percent = access_pa*100,
         latino_percent = percent_hispanic*100) %>%
  ggplot(aes(access_percent, ltpa_percent)) +
  # geom_point(color = 'gray70', alpha = .9) + 
  geom_smooth(method = 'lm', se = FALSE, aes(color = latino_group)) +
  facet_wrap(~year)

```


3. Z-score and make everything into percentages for analyses
```{r}

```

4. Write out model equations.
```{r preliminary physical activity, echo = TRUE, eval = FALSE}
# names(county)

preliminary_ltpa_long <- lmer(ltpa_percent ~ year + (1|county_fips_code), 
                       data = county,
                       REML = FALSE,
                    control = lmerControl(optimizer = 'Nelder_Mead'))

summary(preliminary_ltpa_long)

anova(preliminary_ltpa_long, preliminary_ltpa_long_3)
# physical activity over time (random effect of counties)
```

$$ Fixed Effect: LTPA_{ti} = \beta_{0i} + \beta_{1i}(year_{ti}) + \epsilon_{0ti} $$

$$ Random Effect: \beta_{0i} = \beta_0 + \mu_{0i}  $$

$$ Combined: LTPA_{ti} = \beta_0 + \beta_{1}(year_{ti}) + \mu_{0i}(year_{0ti}) + \epsilon_{0ti} $$

$$ Level 2: [\mu_{0i}] \sim N(0, \sigma^2_{\mu0}) $$

$$ Level 1: [\epsilon_{0ti}] \sim N(0,\sigma^2_{\epsilon0}) $$

```{r preliminary access, echo = TRUE, eval = FALSE}

preliminary_access_pa_long <- lmer(access_pa ~ year + (1|county_fips_code), 
                       data = county,
                       REML = FALSE,
                    control = lmerControl(optimizer = 'Nelder_Mead'))

summary(preliminary_access_pa_long)

anova(preliminary_access_pa_long, preliminary_access_pa_long_3)
# access to physical activity over time (random effect of counties)

```

$$ Fixed Effect: AccessPA_{ti} = \beta_{0i} + \beta_{1i}(year_{ti}) + \epsilon_{0ti} $$

$$ Random Effect: \beta_{0i} = \beta_0 + \mu_{0i}  $$

$$ Combined: AccessPA_{ti} = \beta_0 + \beta_{1}(year_{ti}) + \mu_{0i}(year_{0ti}) + \epsilon_{0ti} $$

$$ Level 2: [\mu_{0i}] \sim N(0, \sigma^2_{\mu0}) $$

$$ Level 1: [\epsilon_{0ti}] \sim N(0,\sigma^2_{\epsilon0}) $$

```{r access longitudinal with controls, echo = TRUE, eval = FALSE}
# names(county)

ltpa_long_controls <- lmer(ltpa_percent ~ year + violent_crime +
                                  adult_obesity + some_college +
                                  income_inequality + air_pollution_particulate_matter +
                                  driving_alone_to_work + percent_rural +
                                  (1|county_fips_code), 
                       data = county,
                       REML = FALSE,
                    control = lmerControl(optimizer = 'Nelder_Mead'))

summary(ltpa_long_controls)


anova(preliminary_ltpa_long, ltpa_long_controls)
```

$$ Fixed Effect: AccessPA_{ti} = \beta_{0i} + \beta_{1i}(Year_{ti}) + \beta_{2i}(ViolentCrime_{ti})+ \beta_{3i}(Obesity_{ti}) + \beta_{4i}(SomeCollege_{ti}) + \beta_{5i}(IncomeInequality_{ti}) + \beta_{6i}(AirPollution_{ti}) + \beta_{7i}(DrivingAlone_{ti}) + \beta_{8i}(Rurality_{ti}) + \epsilon_{0ti} $$

$$ Random Effect: \beta_{0i} = \beta_0 + \mu_{0i}  $$

$$ Combined: AccessPA_{ti} = \beta_0 + \beta_{1}(year_{ti}) + \beta_{2}(ViolentCrime_{ti})+ \beta_{3}(Obesity_{ti}) + \beta_{4}(SomeCollege_{ti}) + \beta_{5}(IncomeInequality_{ti}) + \beta_{6}(AirPollution_{ti}) + \beta_{7}(DrivingAlone_{ti}) + \beta_{8}(Rurality_{ti}) + \mu_{0i}(year_{0ti}) + \epsilon_{0ti} $$

$$ Level 2: [\mu_{0i}] \sim N(0, \sigma^2_{\mu0}) $$

$$ Level 1: [\epsilon_{0ti}] \sim N(0,\sigma^2_{\epsilon0}) $$

```{r physical activity included, echo = TRUE, eval = FALSE}

ltpa_long_access <- lmer(ltpa_percent ~ year + violent_crime +
                                  adult_obesity + some_college +
                                  income_inequality + air_pollution_particulate_matter +
                                  driving_alone_to_work + percent_rural + 
                                  access_pa + (1|county_fips_code), 
                       data = county,
                       REML = FALSE,
                    control = lmerControl(optimizer = 'Nelder_Mead'))

summary(ltpa_long_access)

anova(ltpa_long_controls, ltpa_long_access)
```

$$ Fixed Effect: AccessPA_{ti} = \beta_{0i} + \beta_{1i}(Year_{ti}) + \beta_{2i}(ViolentCrime_{ti})+ \beta_{3i}(Obesity_{ti}) + \beta_{4i}(SomeCollege_{ti}) + \beta_{5i}(IncomeInequality_{ti}) + \beta_{6i}(AirPollution_{ti}) + \beta_{7i}(DrivingAlone_{ti}) + \beta_{8i}(Rurality_{ti}) + \beta_{9i}(LTPA_{ti}) + \epsilon_{0ti} $$

$$ Random Effect: \beta_{0i} = \beta_0 + \mu_{0i}  $$

$$ Combined: AccessPA_{ti} = \beta_0 + \beta_{1}(year_{ti}) + \beta_{2}(ViolentCrime_{ti})+ \beta_{3}(Obesity_{ti}) + \beta_{4}(SomeCollege_{ti}) + \beta_{5}(IncomeInequality_{ti}) + \beta_{6}(AirPollution_{ti}) + \beta_{7}(DrivingAlone_{ti}) + \beta_{8}(Rurality_{ti}) + \beta_{9}(LTPA_{ti}) + \mu_{0i}(year_{0ti}) + \epsilon_{0ti} $$

$$ Level 2: [\mu_{0i}] \sim N(0, \sigma^2_{\mu0}) $$

$$ Level 1: [\epsilon_{0ti}] \sim N(0,\sigma^2_{\epsilon0}) $$

```{r interaction, echo = TRUE, eval = FALSE}
access_latino_int <- lmer(ltpa_percent ~ year + violent_crime +
                                  adult_obesity + some_college +
                                  income_inequality + air_pollution_particulate_matter +
                                  driving_alone_to_work + percent_rural + 
                                  access_pa*percent_hispanic + (1|county_fips_code), 
                       data = county,
                       REML = FALSE,
                    control = lmerControl(optimizer = 'Nelder_Mead'))

summary(access_latino_int)


anova(ltpa_long_access, access_latino_int)
```

$$ Fixed Effect: AccessPA_{ti} = \beta_{0i} + \beta_{1i}(Year_{ti}) + \beta_{2i}(ViolentCrime_{ti})+ \beta_{3i}(Obesity_{ti}) + \beta_{4i}(SomeCollege_{ti}) + \beta_{5i}(IncomeInequality_{ti}) + \beta_{6i}(AirPollution_{ti}) + \beta_{7i}(DrivingAlone_{ti}) + \beta_{8i}(Rurality_{ti}) + \beta_{9i}(LTPA_{ti}) + \beta_{10i}(LatinoPercent_{ti}) + \beta_{11i}(LTPA*LatinoPercent_{ti}) + \epsilon_{0ti} $$

$$ Random Effect: \beta_{0i} = \beta_0 + \mu_{0i}  $$

$$ Combined: AccessPA_{ti} = \beta_0 + \beta_{1}(year_{ti}) + \beta_{2}(ViolentCrime_{ti})+ \beta_{3}(Obesity_{ti}) + \beta_{4}(SomeCollege_{ti}) + \beta_{5}(IncomeInequality_{ti}) + \beta_{6}(AirPollution_{ti}) + \beta_{7}(DrivingAlone_{ti}) + \beta_{8}(Rurality_{ti}) + \beta_{9}(LTPA_{ti}) + \beta_{10}(LatinoPercent_{ti}) + \beta_{11}(LTPA*LatinoPercent_{ti}) + \mu_{0i}(year_{0ti}) + \epsilon_{0ti} $$

$$ Level 2: [\mu_{0i}] \sim N(0, \sigma^2_{\mu0}) $$

$$ Level 1: [\epsilon_{0ti}] \sim N(0,\sigma^2_{\epsilon0}) $$

5. Look into times for multiple imputations, since there is over 5% of missing data for 
```{r}

```








